\documentclass[pdflatex,sn-mathphys-num]{sn-jnl} % Math and Physical Sciences Numbered Reference Style
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{physics}
\usepackage{tikz}
\usepackage{amsopn}
\usepackage{amstext}
\usepackage{microtype}
\usepackage{xparse}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
% Boxes
\usepackage[most]{tcolorbox}
% Plots (pgfplots provides axis/addplot)
\usepackage{pgfplots}
\usetikzlibrary{intersections}
\usepgfplotslibrary{fillbetween}
\pgfplotsset{compat=1.18}
\NewDocumentCommand{\subsubsubsection}{s m}{%
  \IfBooleanTF{#1}{\paragraph*{#2}}{\paragraph{#2}}%
}
\usetikzlibrary
{arrows.meta, calc, fit, decorations.pathmorphing, decorations.pathreplacing, shapes.geometric, shadings, positioning,
  decorations.markings, patterns}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\title{The Fine-Structure Constant as a Projective Invariant:
Lamb Shift and Schwinger Effect in a Pre-Geometric Framework}
\author*[1]{\fnm{Jérôme} \sur{Beau}}\email{jerome.beau@cosmochrony.org}
\affil*[1]{\orgname{Independent Researcher}, \country{France}}
\date{}

\begin{document}

  \abstract{
    The Lamb shift and the Schwinger effect are among the most precise and conceptually
    challenging predictions of quantum electrodynamics.
    They are conventionally interpreted as consequences of vacuum fluctuations,
    radiative corrections, and non-perturbative instabilities of a dynamical quantum
    vacuum.
    While this interpretation achieves remarkable quantitative success, it leaves
    open fundamental questions regarding the ontological status of the vacuum and the
    origin of renormalization procedures.

    In this work, we propose a unified reinterpretation of these phenomena within a
    relational pre-geometric description, in which all effective physical observables
    emerge from a non-injective projection of an underlying relational substrate.
    From this perspective, vacuum-related effects do not arise from physical excitations
    of an underlying field-theoretic vacuum, but from intrinsic limitations of the
    projection mapping relational configurations to effective spacetime descriptions.

    We show that the Lamb shift can be understood as projective spectral noise, reflecting
    the finite resolvability of highly localized interactions and the coarse-grained
    influence of unresolved relational modes.
    Similarly, the Schwinger effect is reinterpreted as a saturation phenomenon associated
    with the bounded capacity of the projection to transport relational flux under extreme
    field conditions, leading to a breakdown of injectivity and the emergence of new
    effective degrees of freedom.

    A central result of this analysis is a unified structural interpretation of the
    fine-structure constant.
    Rather than appearing as an unexplained fundamental parameter, it emerges as an
    invariant ratio between projective resolution and relational flux capacity, governing
    both atomic-scale spectral corrections and strong-field instabilities.

    This reinterpretation preserves the quantitative predictions of quantum
    electrodynamics while providing a coherent ontological account of its most subtle
    effects.
    It demonstrates that precision QED phenomena can be consistently embedded within a
    pre-geometric relational description, supporting the view that quantum field theories
    operate as effective descriptions of deeper projective constraints rather than as
    fundamental theories of the vacuum.
  }

  \maketitle

  \keywords{
    quantum electrodynamics;
    Lamb shift;
    Schwinger effect;
    vacuum interpretation;
    non-perturbative phenomena;
    emergent spacetime;
    pre-geometric frameworks
  }

  \input{01-introduction}
  \input{02-projective-vacuum}
  \input{03-lamb-shift}
  \input{04-schwinger-effect}
  \input{05-fine-structure-constant}
  \input{06-experimental-constraints}
  \input{07-discussion}

  \section*{Funding}
    The author declares that no external funding was received for this research.

    \bmhead{Acknowledgements}
    The author acknowledges the use of large language models as a supportive tool
    for refining language, structure, and internal consistency during the
    development of this manuscript.
    All conceptual contributions, theoretical choices, and interpretations remain the sole responsibility of the author.

    \bibliography{references}

\end{document}
